Prefetching SPARQL query cacher

### 2016-06-01 dissertation/cache-proxy.tex
add label
Merge the documents
add something about expiry

\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

\include{notasjon}
\include{helpers}
\usepackage[pdftex,linktocpage]{hyperref}
\hyperbaseurl{https://github.com/}

\begin{document}
\title{Prefetching SPARQL query cacher}
\author{Kjetil Kjernsmo}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%0316 Oslo, Norway}

%\email{kjekje@ifi.uio.no}

\maketitle

@@

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based \cite{traits} implementation of the
majority of RFC7234. \pmodule{AtteanX::Endpoint} is an implementation of the
server side of SPARQL 1.1 Protocol.

@@

\bibliography{management,dataprofiles,federation,dynamicity,hypermedia,specs,webarch,practical,semweb,caching,critisism,data,philosophy,benchmarks,rfc,programming,egne}
\bibliographystyle{plain}

\end{document}

>>>>

\chapter{Prefetching SPARQL query cacher}\label{sec:tpfcacheplanning}

@@

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol.

@@
